Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-09-01 paper.tex
Add summary

\maketitle              
% 50-80 words
\begin{abstract}
abstract here
\end{abstract}

>>>>

\maketitle              
% 50-80 words
\begin{abstract}
Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and have come to form a multi-billion dollar industry. But IoT cannot be considered a mere extension of DaaS. Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled Data Marketplaces, trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.

In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, putting not merely the trading records but also the transaction process on the distributed ledgers. This way can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain. In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of device, simultaneously making a verifiable Auth-compliant request to the platform in claim of "being tradable." Later, the verified data will enter data marketplace to be traded. Furthermore, the platform will complete matching, trading and refunding without human intervention in the whole process, and also protect the rights of data providers and consumers through trading policy written on smart contract, and finally apply evolutionary game theory to machine economy.
\end{abstract}
